HGIS Carbonate Results

### 2021-06-23 doc/data_meeting_2021-06-22/data_meeting_2021-06-22.Rmd
Clean up output dataframes.

.right-column[
```{r}
cons_df_sum <- cons_df %>% 
  group_by(Name, fm_consensus) %>% 
  summarize(across(c(fm_corr, sig_fm_corr, Fm_diff, sigma),
                   list(mean = mean, sd = sd)),
            N = n()) %>% 
  ungroup()

@@

```{r}
cons_df %>% 
  filter(Name %in% c("TIRI-I", "C-2", "NOSAMS2")) %>% 
  ungroup() %>% 
  summarize(across(c(sig_fm_corr, Fm_diff, sigma),
                   list(mean = mean, sd = sd)),
            N = n()) %>% 
  select(`Mean Fm difference` = Fm_diff_mean,
         `SD of mean difference` = Fm_diff_sd,
         `Mean Fm error` = sig_fm_corr_mean,
         `Mean Sigma` = sigma_mean,
         `SD of Sigma` = sigma_sd,
         N
         ) %>%  
  #pivot_longer(everything()) %>% 
  gt() %>% 
  tab_header(title = "Summary statisics for reference materials",
             subtitle = "TIRI-I, C-2, and NOSAMS2") %>% 
  fmt_number(3:5, decimals = 4)
```
]

@@

```{r}
ggplot(cons_df, aes(x = Fm_diff, y = fm_corr, color = he12C)) +
  geom_hline(aes(yintercept = fm_consensus), color = "lightblue") +
  geom_hline(data = cons_df_sum, aes(yintercept = fm_corr_mean), color = "darkgray") +
  geom_hline(data = cons_df_sum, aes(yintercept = fm_corr_mean + fm_corr_sd), 
             color = "grey", linetype = "dashed") +
  geom_hline(data = cons_df_sum, aes(yintercept = fm_corr_mean - fm_corr_sd),
             color = "grey", linetype = "dashed") +

>>>>

.right-column[
```{r}
cons_df_sum <- cons_df %>% 
  group_by(Name, fm_consensus) %>% 
  summarize(across(c(fm_corr, sig_fm_corr, fm_diff, sigma),
                   list(mean = mean, sd = sd)),
            N = n()) %>% 
  ungroup()

@@

```{r}
cons_df %>% 
  filter(Name %in% c("TIRI-I", "C-2", "NOSAMS2")) %>% 
  ungroup() %>% 
  summarize(across(c(sig_fm_corr, fm_diff, sigma),
                   list(mean = mean, sd = sd)),
            N = n()) %>% 
  select(`Mean Fm difference` = fm_diff_mean,
         `SD of mean difference` = fm_diff_sd,
         `Mean Fm error` = sig_fm_corr_mean,
         `Mean Sigma` = sigma_mean,
         `SD of Sigma` = sigma_sd,
         N
         ) %>%  
  #pivot_longer(everything()) %>% 
  gt() %>% 
  tab_header(title = "Summary statisics for reference materials",
             subtitle = "TIRI-I, C-2, and NOSAMS2") %>% 
  fmt_number(3:5, decimals = 4)
```
]

@@

```{r}
ggplot(cons_df, aes(x = fm_diff, y = fm_corr, color = he12C)) +
  geom_hline(aes(yintercept = fm_consensus), color = "lightblue") +
  geom_hline(data = cons_df_sum, aes(yintercept = fm_corr_mean), color = "darkgray") +
  geom_hline(data = cons_df_sum, aes(yintercept = fm_corr_mean + fm_corr_sd), 
             color = "grey", linetype = "dashed") +
  geom_hline(data = cons_df_sum, aes(yintercept = fm_corr_mean - fm_corr_sd),
             color = "grey", linetype = "dashed") +
